---
title: "FML Assignment-1"
output: html_document
date: "2024-02-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Source of my Dataset: https://www.kaggle.com/datasets/geoffnel/
Job Postings Dataset

Converting the data into R

```{r}
library(readxl)
```

```{r}
Electric_Vehicle_Population_Data <- read.csv("C:/Users/kavip/OneDrive/Documents/Fundamentals of machine learning/Assignment -1/Electric_Vehicle_Population_Data.csv")
```

```{r}
View(Electric_Vehicle_Population_Data)
```

#Providing the discriptive statistics for the database

```{r}
summary(Electric_Vehicle_Population_Data)
```

#Providing the Qualitative Variables 
```{r}
summary(Electric_Vehicle_Population_Data$VIN..1.10.)
```

```{r}
summary(Electric_Vehicle_Population_Data$County)
```

```{r}
summary(Electric_Vehicle_Population_Data$City)
```

```{r}
summary(Electric_Vehicle_Population_Data$State)
```

```{r}
summary(Electric_Vehicle_Population_Data$Make)
```

```{r}
summary(Electric_Vehicle_Population_Data$Model)
```

```{r}
summary(Electric_Vehicle_Population_Data$Electric.Vehicle.Type)
```

```{r}
summary(Electric_Vehicle_Population_Data$Clean.Alternative.Fuel.Vehicle..CAFV..Eligibility)
```

```{r}
summary(Electric_Vehicle_Population_Data$Vehicle.Location)
```

```{r}
summary(Electric_Vehicle_Population_Data$Electric.Utility)
```

##Providing the Quantitative Variables
```{r}
summary(Electric_Vehicle_Population_Data$Postal.Code)
```

```{r}
summary(Electric_Vehicle_Population_Data$Model.Year)
```

```{r}
summary(Electric_Vehicle_Population_Data$Electric.Range)
```

```{r}
summary(Electric_Vehicle_Population_Data$Base.MSRP)
```

```{r}
summary(Electric_Vehicle_Population_Data$Legislative.District)
```

```{r}
summary(Electric_Vehicle_Population_Data$DOL.Vehicle.ID)
```

```{r}
summary(Electric_Vehicle_Population_Data$X2020.Census.Tract)
```

#Transforming one Qualitative Variable into Quantitative Variable that is Electric utility
```{r}
print(Electric_Vehicle_Population_Data$Electric.Utility)
```

#Log transformation

```{r}
Electric_Vehicle_Population_Data$Electric.Utility <-log(Electric_Vehicle_Population_Data$Model.Year)
```


```{r}
summary(Electric_Vehicle_Population_Data$Electric.Utility)
```

#New data after applying the log transformation
```{r}
print(Electric_Vehicle_Population_Data$Electric.Utility)
```

#Now using Histogram we are plotting one quantitative variable 

```{r}
hist(Electric_Vehicle_Population_Data$Electric.Range,
main="Histogram of Range",
xlab="Range",
ylab="Brand",
col="red",
border="white")
```

#Scatterplot of Electric.Utility to the Model.Year
```{r}
plot(Electric_Vehicle_Population_Data$Electric.Utility, Electric_Vehicle_Population_Data$Model.Year,
main="Scatterplot of Electric.Utility vs Model.Year",
xlab="Electric.Utility",
ylab="Model.Year",
col="blue")
```









